---
title: "R Notebook"
output: html_notebook
---
- Import Google Sheets
```{r}
library(lubridate)
library(stringr)
library(googlesheets)
```
- Gain access authorization to your sheets

```{r}
gs_auth(new_user = TRUE)
```
```{r}
gsSurvey<-gs_key("4/gQBoUAjKBqNMR3yLIBLUi6x52l_1774MydnXIXQarRsM0uTMLIBr6iw")  #download sheet information as an object

classSurvey<-gs_read(gsSurvey,ws=1) #access the 1st worksheet
```
```{r}
#5.4 Data Frame
class(classSurvey)
View(classSurvey)
```
 -不同column 可以有不同屬性
 
```{r}

StuDF <- data.frame(
  StuID=c(1,2,3,4,5),
  name=c("小明","大雄","胖虎","小新","大白"),
  score=c(80,60,90,70,50)
  )
StuDF 
```
- name認定為factor(欄位為純文字時容易認定為類別)
```{r}
as.character(StuDF$name) ->StuDF$
```
- 或是可以直接加stringasfacotr = F


#5.4.2 Column/Row names
 1. Column names
```{r}
names(StuDF) 
colnames(StuDF)
```
- names() is more general than colnames, which can be applied to objects other than data frames.

- 檢查classSurvey的變數名稱。
 2. Row names
```{r}
rownames(StuDF)
```
- 檢查classSurvey的rownames。

#5.4.3 Extract observations: numerical/logical index

 1. by matrix index
```{r}
StuDF[1,2]
StuDF[,2]
StuDF[1,]
StuDF[c(1,4),]
StuDF[c(1,4),c(2,3)]
```
- Compare the following two
```{r}
StuDF[c(1,4),]
StuDF[-c(1,4),]
```
- 請使用matrix index來產生head(classSurvey)的結果。
2. by TRUE/FALSE
```{r}
StuDF[c(T,F,F,F,F),c(F,T,F)]
StuDF[c(T,F,F,T,F),]
```
- T代表要選近來/F代表不要
but not True, true, TRue, False, false, FAlse, etc.
- 1:yes, 0:no
apply sum() gives you the total number of TRUEs.

Q Reproduce StuDF[1,] and StuDF[c(1,4),c(2,3)] using T/F method.
```{r}

```
